Legacy Data Confounds Genomics Studies

### 2019-07-12 LatexManuscript/legacy.tex

We therefore performed the same reverse GWAS approach in all populations independently, and similarly identified $Q$-associated SNPs in 23 of the 26 populations in the 1kGP, with the phase 1 populations being most affected, with on average four times as many significantly associated sites compared to the phase 3 populations.
Over 812 variants were independently associated to low $Q$ in at least two populations with $ p < 10^{-6}$ in each.

@@

\caption{Comparing results from the single population tests, we find 812 variants independently associated with average quality of mapped bases $Q$ in more than one population.
\textbf{A} For each population, we plot the number of variants associated to at least one other population.
\textbf{B} The number of populations for which a variant has reached significance.}
  \label{OverLap}
\end{figure}

>>>>

We therefore performed the same reverse GWAS approach in all populations independently, and similarly identified $Q$-associated SNPs in 23 of the 26 populations in the 1kGP, with the phase 1 populations being most affected, with on average four times as many significantly associated sites compared to the phase 3 populations.

\sgcomment{initially was: Over 812 variants were independently associated to low $Q$ in at least two populations with $ p < 10^{-6}$ in each.}

Over 1,165 variants were independently associated to low $Q$ with $ p < 10^{-6}$ in each (Figure \ref{OverLap}).

@@

\caption{Results from the single population test. We find a total of 1,165 variants associated with the average quality of mapped bases $Q$.
Phase 1 populations are indicated by a star ( * ).
\textbf{A} For each population, we plot the number of variants associated to $Q$.
\textbf{B} The number of populations for which a variant has reached significance.}
  \label{OverLap}
\end{figure}
